---
title: "data412_HW1_sydneyball"
author: "Sydney Ball"
date: "`r Sys.Date()`"
output: html_document
---

#Question 1:
Use and show R code to produce all even integers greater than 7 but less than 101
```{r}
seq(8, 100, 2) 
```

#Question 2:
Use and show R code to find the mean of all positive integers less than 100.
```{r}
mean(1:99)
```

#Question 3:
Write a function (using R code and the structure demonstrated in class) to
calculate a z-score for a given observed value, a mean, and a standard deviation
value. And then use your function to find a z score for the following problem.
(Research the internet to find the formula used to calculate a z score)

Observed value = 25.77, mean = 23.54, standard deviation = 2.442
```{r}
zscore<- function(o,m,sd)
  {result <- ((o-m)/sd)
    return(result)
}
zscore(25.77, 23.54, 2.442)
```

#Question 4: 
Use and show R code to round your z score answer in problem 3 to the nearest
tenth.
```{r}
round(.9131859, digits = 3)
```

#Question 5:
Write a function (using R code and the structure demonstrated in class) to
calculate the natural log of a number multiplied by the common log of the same
number divided by the cube root of a given prime number.

Use your function to find the answer if the number to be used for both log
expressions is 32 and the given prime number is 11.
```{r}
numberLog <- function(log,log10,cuberoot)
  {result <- ((log*log10)/(cuberoot))
    return(result)
    }

numberLog (32, 32, 11)

(log(32)*(log10(32)))/(11^(1/3))
```

#Question 6:
Use and show R code to round your answer in problem 5 to the nearest
hundredth.
```{r}
round(2.345548, digit = 2)
```

#Question 7:
Write a function (using R code and the structure demonstrated in class) that will
create the first 10 squares of positive odd integers. Your function should give you
the following output. 1, 9, 25, 49, …, 361 when you input values 1 to 10.
```{r}
list <- c()
for (n in seq(1, 10)) {
    y = 2*n-1
    list[[n]] <- y*y
  }

for (n  in list) {
	print(n)
  }
```











