---
title: "HW#10B"
author: "Sydney Ball"
date: "`r Sys.Date()`"
output: html_document
---

### Question 1:
#### What happens if you use switch() with numeric values?
Using switch() allows you to select an argument with a number. If arguments were products in a vending machine where you can choose what you want, then the numbers are the buttons on the machine that allows you to order what you want from the vending machine. 

### Question 2:
#### Implement a fizzbuzz function. It takes a single number as input. If the number is divisible by three, it returns “fizz”. If it’s divisible by five it returns “buzz”. If it’s divisible by three and five, it returns “fizzbuzz”. Otherwise, it returns the number. Make sure you first write working code before you create the function.
```{r}
fizzbuzz <- function(number_q2) {
  if (number_q2 %% 3 == 0 && number_q2 %% 5 == 0) {
    return("fizzbuzz")
  } else if (number_q2 %% 3 == 0) {
    return("fizz")
  } else if (number_q2 %% 5 == 0) {
    return("buzz")
  } else {
    return(as.character(number_q2))
  }
}
```

### Question 3:
#### What does commas(letters, collapse = "-") do? Why? How can this be corrected? Recall from class that the commas function is as follows:
```{r}
commas <- function(...) {
  str_c(..., collapse = ", ")
}
```
The given code above does not work because it misunderstands the purpose of the function and given number of arguments because there is no explicitly defined collapsing character like a '-' or a ','. Furthermore the function does not understand that we can to separate the letters by '-', it will default to separate the letters by a ','. 

To fix this code, we would wan to move the collapse up into the argument of the function. And then keep collapse in the body of the function to call collapse to collapse the defined varaible argument. Then we can ensure the letters with collapse with a '-' as defined in the argument. 
```{r}
commas <- function(..., collapse = ", ") {
  str_c(..., collapse = collapse)
}
```

### Question 4:
#### It’d be nice if you could supply multiple characters to the pad argument, e.g. rule("Title", pad = "-+"). Why doesn’t this currently work? How could you fix it?
```{r}
rule <- function(..., pad = "-") {
  title <- paste0(...)
  width <- getOption("width") - nchar(title) - 5
  cat(title, " ", str_dup(pad, width), "\n", sep = "")
}
```
I believe that using the command rule() with the use of pad can be used to produce a printed title in a pleasing way with multiple characters. However when you expect to print the rule() title using the pad/bordering argument, the function is not correctly structured to receive the output you want. The code that prints is not aware of the width in which it should repeat the pattern to be the most pleasing. To fix this code, you need to edit the code so that it fills the width of the printing space. 

Something like this:
```{r}
rule <- function(..., pad = "-") {
  title <- paste0(...)
  totalWidth <- getOption("width")
  padLength <- nchar(pad)
  titleWidth <- nchar(title) + 2
  
  padWidth <- totalWidth - titleWidth
  
  completePad <- substr(rep(pad, length.out=padWidth), 1, padWidth)
  
  cat(title, " ", completePad, "\n", sep = "")
}
```
In the function above, I have added a space around the title when printed for visual purposes. Furthermore, I calculated the width minus the title width and then you repeate the printed pattern fro the remainder of the exact width of the space given. This ensures that the visual pattern fits the space in the most visually aesthetic manner. 

### Question 5:
#### What does the trim argument to mean() do? When might you use it?
When you trim the mean() this function would allow you to exclude a percentage of the data to calculate the mean. So you could exclude the top and bottom most 25% percent of the data to be left with the middle 50% which you can calculate the mean from. You may want to use this function in the event that you have many outliers and you simply want to analyze more normal data. 

### Question 6:
#### The default value for the method argument to cor() is c("pearson", "kendall", "spearman"). What does that mean? What value is used by default?
For the default argument for the method cor() being c("pearson", "kendall", "spearman"), mean that there is a multifaceted way for you to observe how things move together in a linear pattern. For 'pearson' argument it would only look at the movement of two variables together in a straight line--the linear correlation of two variables. The 'kendall' argument would allow you to look at the two variables as they rank in order--so how these two variables co-vary. The 'spearman' argument is similar to the 'kendall' argument, but 'spearman' sort of analyzes the marginal increase rather than the total--the monotonic relationship meaning the relationship that neither increases or decreases over time. 









