---
title: "HW#2_Data412_SydneyBall"
author: "Sydney Ball"
date: "`r Sys.Date()`"
output: html_document
---

### Libraries
```{r}
library(tidyverse)
library(ggplot2)
data("midwest")
```

## Question 1
Analyze the data set of "midwest"
```{r}
view(midwest)
help(midwest)
dim(midwest)[1] # ncolumns
dim(midwest)[2] #nrows
```
There are 437 rows and 28 columns in the midwest data set. This means that there are 28 variables in the data. Three categorical in the data are state, inmetro, and county. The variable percollege is the percent of people who are college educated.  

## Question 2
Histogram for poptotal
```{r}
ggplot(data = midwest) +
  geom_histogram(mapping= aes(x=poptotal), binwidth = 1000)
```

## Question 3
Produce a boxplot for area. Then find Q1, Q2, and Q3.
```{r}
ggplot(data = midwest) +
  geom_boxplot(mapping = aes(y=area), color = "lightpink2") +
  coord_flip()

summary(midwest$area)
```
Once the boxplot is found, we can then find the 5 number summary for the quartiles. For Q1 we find that the area is .02400, Q2 is .0300, and Q3 is .03800 in terms of people, but the unit of people is not listed. 

## Question 4
```{r}
ggplot(data = midwest) +
  geom_boxplot(mapping = aes(x=state, y=area), color = "magenta4") 
```

## Question 5
Scatterplot for popdensity and popwhite
```{r}
ggplot(data = midwest) +
  geom_point(mapping = aes(x=popdensity, y=popwhite), color = "skyblue2") +
  xlab("Population Density") +
  ylab("Precentage of Population White") +
  ggtitle("Population density and Race (White)")
```

## Question 6
Smooth line scatter plots for the same scatter plot in question 5
```{r}
ggplot(data=midwest) +
  geom_point(mapping = aes(x = popwhite, y=popdensity), color = "navy") +
  geom_smooth(mapping = aes(x = popwhite, y=popdensity))
```

## Question 7
Another more specfici scatterplot
```{r}
ggplot(data=midwest) +
  geom_point(mapping = aes(x=popwhite, y=popdensity), color = 'red') +
  xlab("White Population") +
  ylab("Population Density") + 
  ggtitle("Population: White vs Density Scatterplot") +
  geom_smooth(method=lm, mapping=aes(x=popwhite,y=popdensity), color = 'brown4') 
```

## Question 8
Write the code that will develop this scatterplot with the smooth regression lines
```{r}
ggplot(data=mpg) +
  geom_point(mapping = aes(x = displ, y=hwy, color = drv)) +
  geom_smooth(mapping = aes(x = displ, y=hwy, color = drv))
```

## Question 9
Develop code that will produce a facet grid of population density by state 
```{r}
ggplot(data=midwest, mapping=(aes(x=state,y=popdensity))) +
  geom_point() +
  facet_wrap(~state) 
```
I am not quite sure what the independent variable on the x-axis is because there is no label in the image. I tried to problem solve with different variables but couldn't find a fit.

## Question 10
Develop the code that produces the facet grid of count of people per city by county. 
```{r}
ggplot(data = mpg) +
  geom_histogram(mapping= aes(x=cty), fill = 'green', binwidth = 1) +
  facet_grid(drv~cyl)
```





