---
title: "HW3_Data412_SydneyBall"
author: "Sydney Ball"
date: "`r Sys.Date()`"
output: html_document
---

##Libraries
```{r}
library("reshape2")
library("tidyverse")
```

##1 Data frame "Tips"
```{r}
?tips
tips.data = reshape2::tips
```
The variable size from data frame "tips" is the size of the party in terms of what a waiter recorded from a restaurant. 

##2 
Mimic the shown bar graph with x = size, y = count and fill the bars with red
```{r}
ggplot(data=tips.data) +
  geom_bar(mapping = aes(x=size, fill=size), color = "red", fill= "red") +
  ggtitle("Bargraph showing counts for tip sizes")
```

##Question 2
Make a stacked bargraph from the bargraph above 
```{r}
cp <-ggplot(data = tips.data, aes(x="", y = size, fill=day))+
  geom_bar(width = .5, stat = "identity")
cp
```

##Question 4
create a pie chart from the data above
```{r}
pie <- cp + coord_polar("y", start=0) 
pie
```

##Question 5
Create a scatterplot using the tips data frame where x = total bill and y = tip/total bill 
```{r}
ggplot(data = tips.data) +
  geom_point(mapping = aes(x=total_bill, y=(tip/total_bill)), color = "maroon2") +
 xlab("Total Bill") +
 ylab("Tips divided by Total Bill") +
 ggtitle("Relationship between tips and the bill total")

```

##Question 6
Make this data into a facet scatter plot graph using day that has 2 rows 
```{r}
ggplot(data=tips.data, mapping=(aes(x=total_bill,y=(tip/total_bill), color = "maroon2"))) +
  geom_point() +              
  facet_wrap(~day, nrow = 2) 
```
It seems that Sunday has a very influential outlier in terms of tip/bill and the total bill.  

##Question 7
Make this data into a facet scatter plot graph using day that has 2 rows 
```{r}
ggplot(data=tips.data, mapping=(aes(x=time,y=size))) +
  geom_point() +              
  facet_wrap(~day, nrow = 2) 
```
It seems that dinner on Sunday is very busy and lunch on Thursday. 

##Question 8
Change the day names in the facet graphs
```{r}
tips.data$day <- factor(tips.data$day, levels = c("Fri", "Sat", "Sun", "Thur"),
                       labels = c("Friday", "Saturday", "Sunday", "Thursday"))

ggplot(data=tips.data, mapping=(aes(x=time,y=size))) +
  geom_point() +              
  facet_wrap(~tips.data$day, nrow = 2)
```



