---
title: "HW5"
author: "Sydney Ball"
date: '`r Sys.Date()`'
output: html_document
---

```{r message=FALSE}
library(tidyverse)
library(Lahman)
```

#### Question 1:
Shoe that Batting is not a tibble.
```{r}
is_tibble(Batting)
```

#### Question 2:
Without hard coding, show the number of rows and columns in Batting.
```{r}
dimensions <- dim(Batting)

dimensions[1]

dimensions[2]
```

#### Question 3:
Convert the data frame from Batting into a tibble.
```{r}
as_tibble(Batting) -> BattingT
is_tibble(BattingT)
```

#### Question 4:
se dplyr coding to determine how many and which players hit more than 30 home runs in 1991. (Select playerID, teamID, yearID, and HR)
```{r}
BattingT%>%
  select(playerID, teamID, yearID, HR)%>%
  filter(HR>=30)%>%
  filter(yearID == 1991)
```

#### Question 5:
Use subsetting R code to determine the mean for HR in 1991.

We determine that the mean number of homeruns in 1991 is about 34.6.
```{r}
BattingT%>%
  select(playerID,teamID,yearID, HR)%>%
   filter(HR>=30)%>%
  filter(yearID == 1991)%>%
  summarize(HR = mean(HR , na.rm = TRUE) ) 
```

#### Question 6:
Use dplyr code to determine how many and which players hit more than 40 SB in 1990. (Select playerID, teamID, yearID, and HR)
```{r}
BattingT%>%
  select(playerID, teamID, yearID, HR, SB)%>%
  filter(SB>40)%>%
  filter(yearID == 1990)
```

#### Question 7:
Use subsetting R code to determine the mean for SB in 1990.
```{r}
BattingT%>%
  select(playerID,teamID,yearID,HR,SB)%>%
   filter(SB>40)%>%
  filter(yearID == 1990)%>%
  summarize(SB = mean(SB , na.rm = TRUE) ) 
```

#### Question 8:
Use R code to create side by side boxplots showing greater than 23HR counts for players in 1990 and 1991.
```{r}
filtered_data <- BattingT %>%
  select(playerID, yearID, HR)%>%
  filter(yearID %in% c(1990, 1991))%>%
  filter(HR > 23)%>%
  arrange(desc(HR))

filtered_data

ggplot(filtered_data, aes(x = as.factor(yearID), y = HR)) +
  geom_boxplot(fill = "green4") +
  labs(x = "Year", y = "Home Run Count", title = "Players with more than 23 Home Runs in 1990 and 1991")
```

#### Question 9:
The boxplots below summarize the combined homerun output for individual players for the years 1990 and 1991. (The individual players on indicated teams who hit more than 23 homeruns)
```{r}
filtered_data2 <- BattingT %>%
  select(playerID, yearID, HR, teamID)%>%
  filter(yearID %in% c(1990, 1991))%>%
  filter(HR > 23)%>%
  arrange(desc(HR))

filtered_data2

ggplot(filtered_data2, aes(x = as.factor(teamID), y = HR)) +
  geom_boxplot(fill = "purple") +
  labs(x = "Team", y = "Home Runs", title = "Boxplot showing more than 23 HRs in 1990 and 1991")
```



























