---
title: "HW6"
author: "Sydney Ball"
date: "`r Sys.Date()`"
output: html_document
---
### Libraries
```{r message=FALSE}
library(tidyverse)
library(devtools)
```

### Code:
```{r}
ut_ld <- untidydata::language_diversity
view(ut_ld)
```
devtools::install_github("jvcasillas/untidydata")

### Question 1:
The data set is too long (444 rows) and should be wider in order to become more useful and understandable. Use and show R code to produce a table that is a wider data table version of the original data table.
```{r}
ut_ld %>% 
  pivot_wider(names_from = Measurement, values_from = Value) ->ut_ld2
ut_ld2
```

### Question 3:
Now use and show R code that will arrange the Continents in alphabetical order. Print the first 40 rows. A partial table showing rows 35 – 40 is given below.
```{r}
ut_ld2%>%
  arrange(Continent) %>% 
  print(n=40) ->ut_ld3
```

### Question 4:
Now use and show R code that will only produce Asian countries in the data table. There are 16 Asian countries.
```{r}
ut_ld3 %>% 
  filter(Continent == "Asia")

```

### Question 5:
Enter the R code untidydata and then select pre_post You should produce the following R data call of untidydata::pre_post Produce the pre_post table that shows all 16 rows.
```{r}
pre_post1 <-untidydata::pre_post 
pre_post1 
  
```

### Question 6:
For the pre_post data table, Use and show R code that will eliminate the under scores for the variable spec. 
```{r}
pre_post1 %>%
  mutate(spec = gsub("_", "", spec))
```

### Question 7:
Use and show R code that imports thespread sheet into R. Assign your imported
data to the variable covid.
```{r}
library(readr)
time_series_covid19_confirmed_global <- read_csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv")

coivd19 <- time_series_covid19_confirmed_global
```

### Question 8: 
The covid data table is too wide. Apply and show R tyding code that will create a longer data table and then print 25 rows of the new data table. A partial table is given below.
```{r}
coivd19 %>% 
  pivot_longer(cols = -c("Province/State", "Country/Region", "Lat", "Long"), 
               names_to = "Date", 
               values_to = "Cases") %>% 
  print(n=25) -> covid19_1

```

### Question 9:
Now use and show R code that changes your table from number 8 and will produce a table that only shows data for the countries Vietnam, Thailand, and Singapore. When printed, the first ten rows automatically show data for Singapore.
```{r}
covid19_1 %>% 
  filter(`Country/Region` %in% c("Vietnam", "Thailand", "Singapore")) %>%
  arrange(`Country/Region`) %>% 
  print(n=10) ->covid19_2
```

### Question 10:

#### 10.A
Use and show R code to find the date on which Singapore experienced 12,693 cases (Code so that a data table shows relevant variables and the answer in the console) Indicate what the answer is.
```{r}
covid19_2 %>% 
  filter(Cases == 12693)
```
  It seems that Singapore experienced 12,693 cases on 4/25/20.

#### 10.B
Use and show R code to find the maximum number of covid-19 cases experienced by the country of Thailand (Code so that a data table shows relevant variables and the answer in the console) Indicate what the answer is.
```{r}
covid19_2 %>% 
  filter(`Country/Region` == "Thailand") %>% 
  slice_max(order_by = Cases)
  
```
  It seems that the max number of cases in Thailand was 4,728,182 cases in the month of March 2023. 
  
#### 10.C
Use and show R code to find the total number of cases for all three countries together (Vietnam, Thailand, and Singapore)
```{r}
covid19_2 %>%
  summarize(total_cases = sum(Cases, na.rm = TRUE))
```
  The total number of cases in Vietnam, Thailand, and Singapore was a whopping 7,133,799,088.	

#### 10.D
Use and show R code to find the total number of cases for each of the three countries (Vietnam, Thailand, and Singapore). Indicate what the answer is for each individual country.
```{r}
covid19_2 %>%
  filter(`Country/Region` == "Vietnam") %>%
  summarize(total_cases = sum(Cases, na.rm = TRUE)) ->covid19_V

covid19_2 %>%
  filter(`Country/Region` == "Thailand") %>%
  summarize(total_cases = sum(Cases, na.rm = TRUE)) ->covid19_T

covid19_2 %>%
  filter(`Country/Region` == "Singapore") %>%
  summarize(total_cases = sum(Cases, na.rm = TRUE)) ->covid19_S

print(c(covid19_V, covid19_T, covid19_S))

```
The total COVID cases for Vietnam 4,314,591,370. The total COVID cases for Thailand 2,095,658,184. The total COVID cases for Singapore 723,549,534.





