---
title: "HW8"
author: "Sydney Ball"
date: "`r Sys.Date()`"
output: html_document
---
##Library
```{r message=FALSE}
library(tidyverse)
```

## Question 1:
Use R code to write the content of the string "Alaska" without the quotes.
```{r}
q1_str <- ("Alaska")
noquote(q1_str)
```

## Question 2:
Use R code to combine the strings "bo" , "nan" , "za". Separate each string with a backslash
```{r}
combined_string <- str_c(c("bo", "nan", "za"), collapse = "\\")
combined_string
```

## Question 3:
For the string, "Mississippi" use R code that will extract the third character through the 6th character and all characters in between
```{r}
q3_str <- c("Mississippi")
str_sub(q3_str, 3,6)
```

## Question 4:
Use R code to convert the string “california” to CALIFORNIA (all caps no quotes)
```{r}
q4_str <- c("california")
q4_str2 <- str_to_upper(str_sub(q4_str))
noquote(q4_str2)
```

## Question 5:
Using the common words of stringr :: words, produce R code that will generate all words that start with a u a v or a q
```{r include=FALSE}
stringr ::  words
words
```


```{r}
str_subset(words,  "^[au\av\aq]")
```

## Question 6:
Using the common words of stringr :: words, produce R code that will generate seven letter words that end in t
```{r}
str_subset(words, "^......t$")
```

## Question 7:
Using the common words of stringr :: words, produce R code that will generate words that end al or el.
```{r}
str_subset(words, "(al|el)$")
```

## Question 8:
Use stringr functions in order to capitalize all entries for the variable trans of the mpg data frame.
```{r}
mpg$trans <- str_to_upper(mpg$trans)
head(mpg)
```

## Question 9:
Use a stringr function(s) to find all words that begin with p and end with t from the stringr:words data bank. How many of these words are there?
```{r}
num1 <- str_subset(words, "^[p]")
num2 <- str_subset(words, "[t]$")
union(num1, num2) -> q9
length(q9)
```
There are 207 words that either beging with the letter p or end with the letter t. 

## Question 10:
Use a stringr function to determine how many common words from the stringr::words data bank begin with a v.
```{r}
q10_str <- str_subset(words, "^[v]")
length(q10_str)
```
There are 8 words that being with the letter v from the common words from the stringr::words. 

## Question 11:
Use a string R function and the stringr :: words data set to find all four letter words that have the letter v in any location.
```{r}
 str_view( words, "v")
```

## Question 12:
Use a string R function and the stringr :: words data set to find all words that begin with a vowel and end with a vowel.
```{r}
str_subset(words, "^[aeiou].*[aeiou]$")
```

## Question 13:
Use and show a string R function and the stringr :: words data set to find all words that end in x using the str_subset string r function and the str_detect string r function.
```{r}
words_ending_in_x_subset <- str_subset(words, "x$")
words_ending_in_x_subset
words_ending_in_x_detect <- words[str_detect(words, "x$")]
words_ending_in_x_detect
```

## Question 14:
Use and show a string R function and the stringr :: words data set to find all words that contain the four vowels a, e, i, and o.
```{r}
q14_str <- str_subset(words,  "[a|e|i|o]")
head(q14_str)
```

## Question 15:
Use and show a string R function and the stringr :: words data set to confirm or disprove that the letter q is always followed by the letter u
```{r}
 str_view(words, "qu")
```





















