---
title: "HW9A"
author: "Sydney Ball"
date: "`r Sys.Date()`"
output: html_document
---
```{r message=FALSE}
library(tidyverse)
```

### Question 1:
#### As illustrated in the notes and your book, create a factor that will allow you to sort the vector given according to value from lowest to highest. (Show all work and steps; make sure that your work shows use of the factor function)
```{r}
y <- c("ten", "eight", "twelve", "two", "six", "four")
ordered_levels <- c("two", "four", "six", "eight", "ten", "twelve")
factor(y, levels = ordered_levels)
```

### Question 2:
#### Create a bar graph that will indicate counts for the different religions in the gss_cat data frame. Use a factor function to align the bars in descending order.
```{r}
data("gss_cat", package = "forcats")

religion_counts <- gss_cat %>%
  count(relig, sort = TRUE) 

religion_counts <- religion_counts %>%
  mutate(relig = fct_reorder(relig, n))

ggplot(religion_counts, aes(x = relig, y = n)) +
  geom_bar(stat = "identity") +
  labs(x = "Religion", y = "Count", title = "Counts of Different Religions in GSS")
```

### Question 3:
#### Use the fct_recode function (along with mutate) to change level 'Never married' to 'Never Married'. You are to perform the change on the marital variable of the gss_cat data frame.
```{r}
gss_cat2 <- gss_cat %>%
  mutate(marital = fct_recode(marital,
                              "Never Married" = "Never married"))
summary(gss_cat2$marital)
```

### Question 4:
#### Use the fct_collapse function to create the table given below for the variable marital of the gss_cat data frame.
```{r}
gss_cat3 <- gss_cat %>%
  mutate(marital = fct_collapse(marital,
                                "Notmarried" = c("Never married", "Divorced", "Separated", "Widowed"),
                                "Married" = "Married",
                                "No answer" = "No answer"))

marital_counts <- gss_cat3 %>%
  count(marital) %>%
  filter(marital %in% c("No answer", "Not married", "Married"))

print(marital_counts)

```

### Question 5:
#### Use and show R code to create a data table the shows the mean age for every religion shown in the gss_cat data frame. A partial table is shown below. Your code should produce a table that shows 15 observations.
```{r}
gss_cat %>%
  group_by(relig) %>%
  summarize(meanage = mean(age, na.rm = TRUE), 
            num = n(),
            age = mean(age, na.rm = TRUE)) -> religage

head(religage, 15)
```

### Question 6:
#### Use and show R code to produce the scatterplot shown that graphically relates mean age to each religion
```{r}
religion_age <- gss_cat %>%
  group_by(relig) %>%
  summarize(meanage = mean(age, na.rm = TRUE))

ggplot(religion_age, aes(x = meanage, y = relig)) +
  geom_point() 
```

### Question 7: 
#### Now use the fct_reorder function to improve on the scatter plot produced in #6. Your scatter plot should show a progression of lowest to highest mean ages for each religion.
```{r}
religage <- gss_cat %>%
  group_by(relig) %>%
  summarize(meanage = mean(age, na.rm = TRUE))

ggplot(religage, aes(x = meanage, y = fct_reorder(relig, meanage))) +
  geom_point()
```








