---
title: "HW9B"
author: "Sydney Ball"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

### Question 1: 
#### The medical term pneumonoultramicroscopicsilicovolcanoconiosis is the longest word in the English language. Using this term, apply stringr code that will produce:
```{r}
question1_term <- "pneumonoultramicroscopicsilicovolcanoconiosis"
str_match(question1_term, "volcano")
```

```{r}
str_match(question1_term, "picsilico")
```

### Question 2: 
#### Create a general regular expression that will match the pattern abccba for the string_view coding below. Do not use the specific lettered pattern given. Use only special characters such as parentheses, periods, quotes and backslahes.
```{r}
strings <- c("abcabc", "abbabb", "abbbab", "abccba")
str_view(strings, pattern = "(.)(.)(.)\\3\\2\\1", match = TRUE)
```

### Question 3:
#### For the vector given below, create a string expression that will match all files that end with .xlsx Use R code that features a stringr function to confirm your answer.
```{r}
files = c(
"tmp-project.csv", "project.csv",
"project2-csv-specs.csv", "project2.csv2.specs.xlsx",
"project_cars.ods", "project-houses.csv",
"Project_Trees.csv","project-cars.R",
"project-houses.r", "project-final.xls",
"Project-final2.xlsx"
)

str_match(files, "\\.xlsx$")
```

### Question 4:
#### Using the words data set, create a regular expression that will match words that end with 2 e’s ( such as free or see ). Use R code that features a stringr function to confirm your answer.
```{r include=FALSE}
stringr ::  words
```


```{r}
words[str_detect(words, ".*ee$")]
```

### Question 5:
#### Create a general regular expression that will match words that start and end with the same character. For example: willow, diamond, or executive.
```{r}
matches <- str_detect(words, "^(.).*\\1$")
matched_words <- words[matches]
matched_words
```

### Question 6:
#### Describe in words what the regular expression will match: “(.)(.)(.).*\\3\\2\\1”
Words that would match this regular expression would look like a word that begins with any 3 letters and then the ".*" mean that there can be any other characters (wildcard) in the word--until the last 3 characters. The last letters/characters could be a repeat of the first 3 but backwards order. So it would be like "Syd(anything else)dys" I think. 










