---
title: "Music Through the Modern Centuries"
author: "Sydney Ball & Riley Valashinas"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: yes
    includes:
    toc: yes
    toc_float: yes
    code_download: yes
    theme: spacelab
    highlight: tango
    df_print: kable
editor_options: 
  markdown: 
    wrap: 72
---

-   *We chose not to directly share or embed our data in the HTML
    output, due to the sheer size of the datasets. Instead, we're giving
    others the option to download our datasets if they wish (see line
    12), without overloading their computers and slowing them down more
    by unnecessarily attaching large datasets.*

# Library:

-   We have installed numerous libraries including the Tidyverse, Kable,
    and more to ensure our data analysis and .html are through and look
    aesthetic.

```{r, warning=FALSE,message=FALSE}
library(readxl)
library(tidyverse)
library(patchwork)
library(kableExtra)
library(dplyr)
library(plotly)
```

------------------------------------------------------------------------

# Datasets:

## Dataset: Music from 1950 to 2019

```{r message=FALSE, warning=FALSE}
#MusicDataset <- read_excel("/Users/rileyvalashinas/MusicDataset.xlsx")
MusicDataset <- read_excel("/Users/sydneyball/Desktop/Data 412/project/MusicDataset.xlsx")
```

Data found from Kaggle. This dataset provides a list of lyrics from 1950
to 2019 describing music metadata as sadness, danceability, loudness,
acousticness, etc. Authors also provide some information as lyrics which
can be used to natural language processing.

Citation: Moura, Luan; Fontelles, Emanuel; Sampaio, Vinicius; França,
Mardônio (2020), "Music Dataset: Lyrics and Metadata from 1950 to 2019",
Mendeley Data, V3, doi: 10.17632/3t9vbwxgr5.3

[Link to Music Dataset
1950-2019](https://www.kaggle.com/datasets/saurabhshahane/music-dataset-1950-to-2019/code)

## Dataset: Top Songs in the World

```{r, warning=FALSE,message=FALSE}
#Top_Song <- read_excel("/Users/rileyvalashinas/Top Songs in the World.xlsx", 
    #skip = 1)
Top_Song <- read_excel("/Users/sydneyball/Desktop/Data 412/project/Top Songs in the World.xlsx", 
      skip = 1)
```

Dataset was also found on Kaggle. "Top Songs of the World" is a
collection of information about popular songs spanning various decades
and genres. The dataset includes details such as the ranking of songs,
the respective artists, titles, release years, sales figures, streaming
statistics, download counts, radio play metrics, and a numerical rating.

[Link to Top Songs in the World
Dataset](https://www.kaggle.com/datasets/shiivvvaam/top-songs-of-the-world/data)

------------------------------------------------------------------------

# Dataset Breakdown:

## Music Dataset 1950-2019:

### Structure:

```{r}
view(MusicDataset)
length(col(MusicDataset))
```

-   There are 851160 observations

```{r}
length(MusicDataset)
```

-   There are 30 columns.

In the Music 1950-2019 there are 851160 original unique
observations/rows within the data. There are also 31 columns or
variables that are measured within the data.

### Column names:

-   Here we look at the names of all of the columns in the dataset.

```{r}
column_names_1 <- names(MusicDataset)
print(column_names_1)
```

### Artist Names:

-   Artists name = categorical (mostly unique values)

    -   We see that there are some artists whose names are repeated
        because that have many songs which appear on the dataset.

    ```{r}
    artist_count <- MusicDataset %>%
      group_by(artist_name) %>%
      summarise(Count = n()) %>%
      arrange(desc(Count))

    top_20_artists <- artist_count %>%
      top_n(20, Count)

    ggplot(top_20_artists, aes(x = reorder(artist_name, Count), y = Count)) +
      geom_col(fill = "blue4") +
      geom_text(aes(label = Count), position = position_dodge(width = 0.9), hjust = -0.2, size = 3) +
      coord_flip() +
      labs(title = "Top 20 Songs by Artists from 1950 to 2019",
           x = "Artist",
           y = "Count of Top Songs") +
      theme_minimal()
    ```

    -   This graph illustrates the top 20 artists in the Music Dataset
        based on their commonality in the spreadsheet.

### Track Name:

-   Track Name = categorical (unique value) Release date = categorical
    (years 1950 till 2019)

### Release Date:

-   Release date in this dataset ranges from 1950-2019 strictly. However
    there is a denser distribution of songs published in the later 1975
    to the early 2000s.

```{r}
ggplot(MusicDataset, aes(x = release_date)) +
  geom_histogram(binwidth = 1, fill = "skyblue2", color = "blue4") +
  theme_minimal() +
  labs(title = "Distribution of Song Releases Over Time",
       x = "Release Year",
       y = "Count of Songs")
```

### Genre:

-   Genre = categorical (blues, country, hip hop, jazz, pop, reggae,
    rock)

```{r, warning=FALSE,message=FALSE}
table(MusicDataset$genre)
```

### Lyrics:

-   Lyrics = All the lyrics in a single song

### Descriptive Varaibles:

-   Descriptive variables = The remaining 23 decimal variables are
    measured on a ratio decimal scale--this is not evidential, but human
    observation.

### Topic:

-   Topic = Categorical based on feelings, music night/time, obscene,
    romantic, sadness, violence, world/life

```{r, warning=FALSE,message=FALSE}
table(MusicDataset$topic)
```

### Variable Breakdown:

The total break down for the Music Dataset from 1950 to 2019 is: - 23
decimal variables - 5 string variables - 3 integer variables

------------------------------------------------------------------------

## Top Song:

### Structure:

```{r, warning=FALSE,message=FALSE}
length(col(Top_Song))
```

-   There are 38800 observations.

```{r, warning=FALSE,message=FALSE}
length(Top_Song)
```

-   There are 8 columns.

In the Top Songs in the world dataset there are 38800 observations or
top songs. There are also 8 columns or variables which the songs are
measured by.

### Columns names:

```{r, warning=FALSE,message=FALSE}
column_names_2 <- names(Top_Song)
print(column_names_2)
```

### Artist Names:

-   Artist = Includes all the names of artists in the top_songs

    -   It is important to note that some artist names will occur twice
        due to the artist having a top song more than once.

    ```{r, warning=FALSE,message=FALSE}
    artist_counts_2 <- Top_Song %>%
      group_by(Artist) %>%
      summarise(Count = n()) %>%
      arrange(desc(Count))

    top_20_artists_2 <- artist_counts_2 %>%
      top_n(20, Count)

    ggplot(top_20_artists_2, aes(x = reorder(Artist, Count), y = Count)) +
      geom_col(fill = "skyblue2") +
      geom_text(aes(label = Count), position = position_dodge(width = 0.9), hjust = -0.2, size = 3) +
      coord_flip() +
      labs(title = "Top 20 Artists by Number of Top Songs",
           x = "Artist",
           y = "Count of Top Songs") +
      theme_minimal()
    ```

    -   This graph illustrates the top 20 artists on the top songs data
        set and a count of their tops songs.

### Track Names:

-   Title = qualitative name of the song Year = categorical year song
    was published

```{r, warning=FALSE,message=FALSE}
ggplot(Top_Song, aes(x = Year)) +
  geom_histogram(binwidth = 1, fill = "skyblue2", color = "blue4") +
  theme_minimal() +
  labs(title = "Distribution of Top Songs Releases Over Time",
       x = "Release Year",
       y = "Count of Songs")
```

-   This graph highlights the release years of songs in the dataset. We
    see that the bulk of songs in the spreadsheet are comprised from the
    late 1950s to the early 2000s.

### Relase Year:

-   Asses the range of release years

```{r, warning=FALSE,message=FALSE}
max_year <- max(Top_Song$Year, na.rm = TRUE)
min_year <- min(Top_Song$Year, na.rm = TRUE)
print(paste("The range of years is from", min_year, "to", max_year))
```

### Sales:

-   Sales = quantitative The total sales figure for each song

### Streams:

-   Streams = quantitative The number of streams the song has received.

### Downloads:

-   Downloads = quantitative The number of downloads for the song.

### Radio Plays:

-   Radio Plays = quantitative The number of times the song has been
    played on the radio.

### Rating:

-   Rating = quantitative A numerical rating or score associated with
    the song.

------------------------------------------------------------------------

# Clean Data:

## Music Dataset 1950-2019 Cleaning:

```{r, warning=FALSE,message=FALSE}
#Convert columns into proper variable category
MusicDataset$release_date <- as.Date(MusicDataset$release_date, format = "%Y")

#Get rid of any missing values
MusicDataset <- na.omit(MusicDataset)

#Remove any and all duplicates
MusicDataset <- MusicDataset[!duplicated(MusicDataset), ]

#Standardize all text in the data set
MusicDataset$genre <- tolower(MusicDataset$genre)
```

-   We have cleaned the Music Dataset by:
    -   converting the columns into the proper variable category
    -   then removing any missing values. Its important to note that our
        data was found on Kaggle and was already quite clean.
    -   We then removed possible duplicates and standardized the text in
        the data. All of these decisions are stand moves when cleaning a
        large dataset.

## Top Song Cleaning:

```{r, warning=FALSE,message=FALSE}
#Standardize the column names to ensure names are consistent and descriptive
colnames(Top_Song) <- c("Artist", "Title", "Year", "Sales", "Streams", "Downloads", "RadioPlays", "Rating")

#Make sure the variable 'Year' is numeric
Top_Song$Year <- as.numeric(Top_Song$Year)

#Remove any of the missing values in the data set
Top_Song <- na.omit(Top_Song)
Top_Song$Sales <- ifelse(is.na(Top_Song$Sales), mean(Top_Song$Sales, na.rm = TRUE), Top_Song$Sales)

#Remove any possible duplicates from the data
Top_Song <- na.omit(Top_Song)
Top_Song$Sales <- ifelse(is.na(Top_Song$Sales), mean(Top_Song$Sales, na.rm = TRUE), Top_Song$Sales)

#We decided to standardize the printing of all artist names
Top_Song$Artist <- tolower(Top_Song$Artist)

#Remove possible outliers in the data
Top_Song <- subset(Top_Song, Sales <= quantile(Sales, 0.99))
```

-   For the Top Songs dataset we:
    -   decided to first rename all the columns, name sure the column
        year is a numeric variable. - We then moved through standard
        procedure of removing missing values and duplicate values. -
        Finally we standardized all the text and found that there could
        be possible outliers within the data and removed those for more
        standardized usage.

Is the data (Music Dataset & Top Songs) clean enough? - To ensure that
the both datasets were cleaned well and to a standard which we can then
use them to do more statistical analysis we look at the sums of omitted
values in each column.

```{r, warning=FALSE,message=FALSE}
colSums(is.na(MusicDataset))
colSums(is.na(Top_Song))
```

------------------------------------------------------------------------

# Make the cleaned data into Tribble:

-   Then we make the clean datasets into a tribble to be able to
    manipulate easier and observe a small amount of the data in an easy
    to read format.

```{r, warning=FALSE,message=FALSE}
clean_MusicDataset <- as_tibble(MusicDataset)
clean_topSong <- as_tibble(Top_Song)
```

------------------------------------------------------------------------

# Characterize data

-   We call the summary of each cleaned dataset and we also assess the
    structure of the data now that it is renamed and all the n/a
    observations are cleared.

```{r include=FALSE}
#Summarize the data
summary(clean_MusicDataset)
summary(clean_topSong)

#Observe the structure of the data
str(clean_MusicDataset)
str(clean_topSong)
```

-   We characterize the data to make sure that all our cleaning was
    effective and to understand the spread of the data and observations.
    Characterizing the data also allows us to better understand possible
    comparisons between variables that we can make. This part is
    critical to our next steps of evidential data analysis.

## Music Dataset 1950-2019

```{r, warning=FALSE,message=FALSE}
#Mean release date
mean_musicdata <- mean(clean_MusicDataset$release_date, na.rm = TRUE)

#Median release date
median_musicdata <- median(clean_MusicDataset$release_date, na.rm = TRUE)

#Standard deviation of release date
sd_musicdata <- sd(clean_MusicDataset$release_date, na.rm = TRUE)

#Print findings
print(paste("The mean number of songs plublished from the Music Dataset from 1950 to 2019 is", mean_musicdata, "and the median is", median_musicdata, "with a standard deviation of", round(sd_musicdata,2),"years."))
```

## Top Song Dataset

```{r, warning=FALSE,message=FALSE}
#Mean release date
mean_topsong <- mean(clean_topSong$Year, na.rm = TRUE)

#Median release date

median_topsong <- median(clean_topSong$Year, na.rm = TRUE)

#Standard deviation of release date
sd_topsong <- sd(clean_topSong$Year, na.rm = TRUE)

#Print findings
print(paste("The mean number of songs plublished from the Top Song dataset is the year", round(mean_topsong,2), "with the median year being", round(median_topsong,2), "with a standard deviation of", round(sd_topsong,2), "years."))
```

-   We found it important to highlight that although these datasets had
    similar topics, the range of music relative to date may be
    different. We have be highly speculative of release date or year of
    publication so far becuase it can help us explain possible outside
    factors ehich infleunce the popularity of music withing the
    population.

------------------------------------------------------------------------

Our main goal is to analyze how different songs provoke different
emotions in listeners. This means our focus is more tailored towards the
Music Dataset from 1950-2019. After we so analysis of this dataset, we
wanted to look at the cross over between emotion illicit from listening
to a song and the possible correlation relationship between popularity.

------------------------------------------------------------------------

# Assess Relationships using ggplots

-   We have put together 3 various bar graphs by date, genre, or topic
    based on the count within the dataset. The bar graphs help us
    characterize and understand the spread of the data.

## Release Year by Topic and Genre

```{r, warning=FALSE,message=FALSE}
plot1 <- ggplot(data = clean_MusicDataset) + 
  geom_bar(aes(x = release_date), fill = "skyblue2") +
  xlab("Date of Release") +
  ylab("Count") +
  ggtitle("Count of Songs Release by Year")

plot2 <- ggplot(data = clean_MusicDataset) + 
  geom_bar(aes(x = genre), fill = "blue4") +
  xlab("Genre") +
  ylab("Count") +
  ggtitle("Count of Songs by Genre")

plot3 <- ggplot(data = clean_MusicDataset) + 
  geom_bar(aes(x = topic), fill = "blue4") +
  xlab("Topic") +
  ylab("Count") +
  ggtitle("Count of Songs by Topic")
  
plot1 / (plot2 + plot3)

```

### Assess Relationship by Numeric Variables:

-   Here we have grouped the relationships we have begun looking at.

### Danceability by Loudness

```{r, warning=FALSE,message=FALSE}
correlation_coefficient1 <- cor(clean_MusicDataset$danceability, clean_MusicDataset$loudness)
plot4 <-ggplot(data=clean_MusicDataset) +
  geom_point(mapping = aes(x = danceability, y= loudness), color = "skyblue2") +
  geom_smooth(mapping = aes(x = danceability, y=loudness), color = "blue4") +
  xlab("Dance Rating") +
  ylab("Loudness/Noise Rating") +
  ggtitle("Dance by Loud Rating", correlation_coefficient1)

plot4a <-ggplot(data = clean_MusicDataset, mapping = aes(x = danceability, y = loudness)) +
  geom_point(color = "skyblue2") + 
  geom_smooth(method = "lm", se = FALSE, color = "blue4") +  
  facet_wrap(~genre) + 
  xlab("Dance Rating") +
  ylab("Loudness/Noise Rating") +
  ggtitle("Dance by Loudness Rating Across Genres")

plot4b <- ggplot(data = clean_MusicDataset, mapping = aes(x = danceability, y = loudness)) +
  geom_point(color = "skyblue2") + 
  geom_smooth(method = "lm", se = FALSE, color = "blue4") +  
  facet_wrap(~topic) + 
  xlab("Dance Rating") +
  ylab("Loudness/Noise Rating") +
  ggtitle("Dance by Loudness Rating Across Topics")

plot4
plot4a
plot4b
```

-   This grouping is danceability by loudness. There are no apparent
    strong relationships among these variables, but we can use some
    statistical tests to determine this for sure. To learn this, we can
    look at r, Pearson's correlation coefficient, and test the
    significance of said correlation. First is the general test; the
    null hypothesis is that there is no statistically significant
    relationship between danceability and loudness.

```{r, warning=FALSE,message=FALSE}
cor.test(clean_MusicDataset$danceability, clean_MusicDataset$loudness)
```

The p-value falls well below the standard significance level of 0.05,
meaning that we can reject the null hypothesis. There is a statistically
significant relationship between danceability and loudness.

We can also see if this holds by genre:
```{r, warning=FALSE,message=FALSE}
genres <- c('blues', 'country', 'hip hop', 'jazz', 'pop', 'reggae', 'rock')
genres_d_l <- for (i in genres){
  newtr <- filter(clean_MusicDataset, genre==i)
  print(i)
  print(cor.test(newtr$danceability, newtr$loudness))
}
```
Every p-value is far below the significance level of 0.05. We can reject the null hypothesis for each level of the variable 'genre', showing that there is a statistically significant relationship between loudness and danceability regardless of genre.

Next, we'll see if it holds by topic. (Note: whereas we used a self-made genres list vector for the genres and redefined it each time, to show a different technique, for all statistics that separate by topic, we'll use this same 'topicsList' variable that we got from the 'unique()' command.
```{r, warning=FALSE, message=FALSE}
topicsList <- unique(clean_MusicDataset$topic)
topicsList
topics_d_l <- for (i in topicsList){
  newtrib <- filter(clean_MusicDataset, topic==i)
  print(i)
  print(cor.test(newtrib$danceability, newtrib$loudness))
}
```
- There are some surprising (and mixed) observations here. We can see that p-values that fall below the significance level of 0.05 correspond to songs with the topics 'violence', 'romantic', 'music', and 'world/life' — in those cases, we can reject the null hypothesis, and be reasonably sure that there is a statistically signfiicant correlation between danceability and loudness. However, p-values that are above the significance level corresponds to songs of the topics 'feelings', 'night/time', 'obscene', and 'sadness' — in those cases, we fail to reject the null hypothesis, and can assume that there is no statistically significant correlation between danceability and loudness.

### Sadness by Feelings

```{r, warning=FALSE,message=FALSE}
correlation_coefficient2 <- cor(clean_MusicDataset$sadness, clean_MusicDataset$feelings)
plot5 <- ggplot(data=clean_MusicDataset) +
  geom_point(mapping = aes(x = sadness, y= feelings), color = "skyblue2") +
  geom_smooth(mapping = aes(x = sadness, y=feelings), color = "blue4") +
  xlab("Sadness Rating") +
  ylab("Feelings Rating") +
  ggtitle("Sadness by Feelings Rating", correlation_coefficient2)

plot5a <-ggplot(data = clean_MusicDataset, mapping = aes(x = sadness, y = feelings)) +
  geom_point(color = "skyblue2") + 
  geom_smooth(method = "lm", se = FALSE, color = "blue4") +  
  facet_wrap(~genre) + 
  xlab("Sadness Rating") +
  ylab("Feelings Rating") +
  ggtitle("Sadness by Feelings Rating Across Genres")

plot5b <-ggplot(data = clean_MusicDataset, mapping = aes(x = sadness, y = feelings)) +
  geom_point(color = "skyblue2") + 
  geom_smooth(method = "lm", se = FALSE, color = "blue4") +  
  facet_wrap(~topic) + 
  xlab("Sadness Rating") +
  ylab("Feelings Rating") +
  ggtitle("Sadness by Feelings Rating Across Topics")

plot5
plot5a
plot5b
```

-   This grouping is sadness by feelings. There are no apparent strong
    relationships among these variables by genre or in general, but we
    can test to make sure using a Pearson's r coefficient, generally and
    by genre. The null hypothesis is that there is no relationship
    between sadness and feelings rating (first in general, second across
    genres).

```{r, warning=FALSE,message=FALSE}
corr_pt2 <- cor.test(clean_MusicDataset$sadness, clean_MusicDataset$feelings)
corr_pt2
```

Here, we can see that at a significance level of 0.05, the p-value is
clearly small enough to reject the null hypothesis. There is clearly a
relationship between sadness and feelings ratings, and we can see from
the plot that that appears to be a negative relationship (so as sadness
rating goes up, feelings rating goes down).

```{r, warning=FALSE,message=FALSE}
genres <- c('blues', 'country', 'hip hop', 'jazz', 'pop', 'reggae', 'rock')
genres_s_f <- for (i in genres){
  newtr <- filter(clean_MusicDataset, genre==i)
  print(i)
  print(cor.test(newtr$feelings, newtr$sadness))
}
```
These results show us that the p-values in each genre were small enough to reject the null hypothesis in every genre except hip-hop, where there does not seem to be a statistically significant relationship between feelings ratings and sadness ratings.

Finally, we'll see if this connection holds at each level of the variable 'topic':
```{r, warning=FALSE, message=FALSE}
topics_s_f <- for (i in topicsList){
  newtribb <- filter(clean_MusicDataset, topic==i)
  print(i)
  print(cor.test(newtribb$sadness, newtribb$feelings))
}
```
We can see that for the topics 'feelings', 'night/time', 'world/life', and 'sadness', the p-value is certainly below the significance level of 0.05. We can reject the null hypothesis, and conclude that for songs about 'feelings', 'night/time', 'world/life', and 'sadness', there is a statistically significant relationship between feelings ratings and sadness ratings, and we can see from the charts that this relationship seems to trend in the negative direction. However, for songs that are 'romantic', 'obscene', or about 'violence' or 'music', this relationship does not hold, as the p-values are not small enough to reject the null hypothesis at a significance level of 0.05.

### Obscene by Romantic

```{r, warning=FALSE,message=FALSE}
correlation_coefficient3 <- cor(clean_MusicDataset$obscene, clean_MusicDataset$romantic)
plot6 <- ggplot(data=clean_MusicDataset) +
  geom_point(mapping = aes(x = obscene, y= romantic), color = "skyblue2") +
  geom_smooth(mapping = aes(x = obscene, y=romantic), color = "blue4") +
  xlab("Obscene Rating") +
  ylab("Romantic Rating") +
  ggtitle("Obscene by Romantic Rating", correlation_coefficient3)

plot6a <-ggplot(data = clean_MusicDataset, mapping = aes(x = obscene, y = romantic)) +
  geom_point(color = "skyblue2") + 
  geom_smooth(method = "lm", se = FALSE, color = "blue4") +  
  facet_wrap(~genre) + 
  xlab("Obscene Rating") +
  ylab("Romantic Rating") +
  ggtitle("Obscene by Romantic Rating Across Genres")

plot6b <-ggplot(data = clean_MusicDataset, mapping = aes(x = obscene, y = romantic)) +
  geom_point(color = "skyblue2") + 
  geom_smooth(method = "lm", se = FALSE, color = "blue4") +  
  facet_wrap(~topic) + 
  xlab("Obscene Rating") +
  ylab("Romantic Rating") +
  ggtitle("Obscene by Romantic Rating Across Topics")

plot6
plot6a
plot6b

```

-   This grouping is by obscene and romantic. Once again there is not
    apparent strong relationship (positive or negative) among these two
    variables by either genre or topic. But it would be helpful to know
    if there is a real relationship between obscenity and romantic
    rating, and if it just appears to have no correlation, so we'll use
    Pearson's r coefficient again. This will test by just obscenity and
    romantic rating as a whole, without looking at any groupings:

```{r, warning=FALSE,message=FALSE}
cor.test(clean_MusicDataset$romantic, clean_MusicDataset$obscene)
```

So we can clearly see that there is a statistically significant
relationship between x, romantic rating, and y, obscenity rating, at a
significance level of 0.05. We reject the null hypothesis, and can see
that there is a relationship between the obscenity and romantic content
of a song. Looking at the graph seems to show that this correlation is
in the negative direction.

- Further, we can start to see if this relationships hold when grouped by genre. The null hypothesis we are testing here is that there is no relationship between romantic content and obscenity content when grouped by genre, at a significance level of 0.05. We'll do this by using a for-loop to separate the data by genre, and then to check the significance of the value of r:

```{r, warning=FALSE,message=FALSE}
genres <- c('blues', 'country', 'hip hop', 'jazz', 'pop', 'reggae', 'rock')
genres_o_r <- for (i in genres){
  newtr <- filter(clean_MusicDataset, genre==i)
  print(i)
  print(cor.test(newtr$obscene, newtr$romantic))
}
```
- We can see that for all seven genres, the r value falls well below 0.05, meaning that we reject the null hypothesis. There is a clear relationship between obscenity and romantic content by genre, and the graphs seem to universally display a negative relationship.

Finally, let's check and see if this relationship holds across topics:
```{r}
topics_o_r <- for (i in topicsList){
  newtribble <- filter(clean_MusicDataset, topic==i)
  print(i)
  print(cor.test(newtribble$obscene, newtribble$romantic))
}
```
We see from the results above that across nearly all topics, we can reject the null hypothesis, indicating that there is a statistically significant relationship between obscenity and romantic content. However, this relationship does not hold for songs about 'feelings'.

### Genre by Length of Song

```{r, warning=FALSE,message=FALSE}
ggplot(data = clean_MusicDataset) +
  geom_boxplot(mapping = aes(x=genre, y=len), color = "blue4", fill = "skyblue2") +
  xlab("Genre") +
  ylab("Length of Song") +
  ggtitle("Length of Song by Genre")

```

-   This boxplot allows us to visualize the distribution of song lengths
    by genre. We see that blues and country have a generally shorter
    song length. Reggae and hip hop are generally longer with high
    median lengths than all other song genres.

```{r, warning=FALSE,message=FALSE}
meanset <- mean(clean_MusicDataset$len)
lens <- clean_MusicDataset%>%
  group_by(genre)%>%
  summarise(sds=sd(len), means=mean(len), zs=((means-meanset)/sds), probs=pnorm(zs))
lens
```

-   But to confirm, we can run some calculations to see if there are
    statistically significant differences in song lengths by genre.
    We've built out this tibble (see above) with all of the component
    pieces of a z-score test of significance (between the average length
    of each song by genre and the average length of all songs in the
    dataset regardless of genre), then extracted from that a p-value.
    The null hypothesis is that there is no difference in song length by
    genre. None of the genres come close to having a statistically
    significant p-value at a significance level of 0.05, so we cannot
    reject the null hypothesis --- there's no evidence to indicate that
    there is a meaningful difference in song length by genre.

------------------------------------------------------------------------

# Combine Data

The data is joined based on Artist name. We first need the mutate the
variable name from the clean Music Dataset because the original name was
artist_name. Now that both data sets have the same name for Artists, we
can inner join the data. In the joined dataset we see that there are
many artists with multiple songs.

```{r, warning=FALSE,message=FALSE}
#We first need to change the column name from the music dataset to match the name in the top songs dataset
clean_MusicDataset <- rename(clean_MusicDataset, Artist = artist_name)

#Inner join the two data sets based on Artist name 
joined_dataset <- inner_join(clean_MusicDataset, clean_topSong, by = "Artist")

#Remove the column track name from the Music Dataset because it messes with the organization of the joined set
joined_dataset_2 <- select(joined_dataset, -track_name, -release_date)

#Rearrange the dataset to make is artist then title then year and the rest of the variables 
final_joined_dataset <- joined_dataset_2 %>%
  select(Artist, Title, Year, everything())
kable(head(final_joined_dataset,1))

#Use the final_joined_dataset for other analysis
```

-   Now that we have joined the cleaned dataset we can now begin to
    characterize the joined data. Here we are analyzing the top artist
    by mean sales, mean stream, mean downloads, and the summary of genre
    distribution among the joined data. Then to further organize the
    data we made sure to organize the distribution of songs by artist in
    descending order--from highest to lowest.

### Average number of Songs per Artist

```{r, warning=FALSE,message=FALSE}
#We then want to get an understanding of how many songs the top artists have in top songs from the music dataset.
artist_song_count <- final_joined_dataset %>%
  group_by(Artist) %>%
  summarise(number_of_songs = n()) %>% 
  arrange(desc(number_of_songs))
kable(head(artist_song_count,15))
```

### Average number of Song Sales per Artist

```{r, warning=FALSE,message=FALSE}
#Artist by sales
artist_sales <- final_joined_dataset %>%
  group_by(Artist) %>%
  summarise(average_sales = mean(Sales,  na.rm = TRUE)) %>% 
  arrange(desc(average_sales))
kable(head(artist_sales, 15))
```

### Average number of Song Streams per Artist

```{r, warning=FALSE,message=FALSE}
#Artist by streams
artist_streams <- final_joined_dataset %>%
  group_by(Artist) %>%
  summarise(average_streams = mean(Streams, na.rm = TRUE)) %>% 
  arrange(desc(average_streams))
kable(head(artist_streams,15))
```

### Average number of Song Downloads per Artist

```{r, warning=FALSE,message=FALSE}
#Artist by downloads
artist_downloads <- final_joined_dataset %>%
  group_by(Artist) %>%
  summarise(average_downloads = mean(Downloads, na.rm = TRUE)) %>% 
  arrange(desc(average_downloads))
kable(head(artist_downloads,15))
```

### Songs by Genre in Descending Order

```{r, warning=FALSE,message=FALSE}
#genre distribution of songs in joined data 
genre_distribution1 <- final_joined_dataset %>%
  group_by(genre) %>%
  summarise(number_of_songs = n())

# Order by descending number of songs
genre_distribution2 <- genre_distribution1 %>% 
  arrange(desc(number_of_songs))
kable(genre_distribution2)

```

-   To understand the distribution of songs per decade in the joined
    data we see certain trends among genres and the time they were
    released. We see that in late 60s there were many rock songs
    released followed closely by pop songs. This dataset appears to show
    a noticeable peak in song publishing in the late 60s to early 70s
    and then the trend among all genres begins to taper off. This could
    be for a few reasons; maybe there really was such a peak and now
    fewer songs are released, or, because we performed an inner join,
    songs that top the charts today aren't represented in the original
    music dataset, or songs are lasting on the charts longer making it
    so that there are fewer unique songs in the top charts dataset these
    days... the list goes on.

```{r}
#Separate code by decade
joined_dataset_deade <- final_joined_dataset %>%
  mutate(decade = floor(Year / 10) * 10)

#Group the data by decade
count_data <- joined_dataset_deade %>%
  group_by(decade, genre) %>%
  summarise(Count = n(), .groups = 'drop') 

# Creating the count plot
ggplot(count_data, aes(x = decade, y = Count, fill = genre)) + 
  geom_bar(stat = "identity", position = "dodge") +
  theme_minimal() +
  labs(y = "Song Count", x = "Decade", title = "Song Count by Decade and Genre") +
  theme(legend.position = "top")
```

------------------------------------------------------------------------

# Use ggplot to observe the data

-   Although we have not focused much on the lyrics variable of each
    song, we thought it was important to at least observe the top most
    used words in lyrics. Here we observe the top 20 words that are most
    often used in songs from the joined dataset. From this we can
    further understand that words like "heart," "life," and "night" are
    commonly used and could potentially have a relationship with the
    feelings and emotions a songs elicits to its listener.

```{r, warning=FALSE,message=FALSE}
words <- final_joined_dataset %>%
  mutate(words = strsplit(as.character(lyrics), "\\s+")) %>%
  unnest(words)

# Step 3 & 4: Count occurrences and arrange
top_words <- words %>%
  count(words, name = "count") %>%
  arrange(desc(count)) %>%
  slice_head(n = 20) %>%
  pull(words) # Pull the 'words' column to get just the word list

# top_words now contains the top 20 most common words
print(top_words)
```

-   The graph below demonstrates the evolution of feelings across
    decades. This interactive plot allows us to view the relationships
    of feelings and the ups and downs of their trends as new songs are
    published, as listeners opinions change, and possible as the world
    reflects on the type of music that is published.

```{r, warning=FALSE,message=FALSE}
data_aggregated <- final_joined_dataset %>%
  mutate(decade = floor(Year / 10) * 10) %>% 
  group_by(decade) %>%
  summarise(across(c(dating, violence, `world/life`, `night/time`, `shake the audience`, `family/gospel`, 
                     romantic, communication, obscene, `family/spiritual`, `like/girls`, sadness, 
                     feelings), ~mean(.x, na.rm = TRUE)))  

# Proceed with transforming to long format
data_long <- data_aggregated %>%
  pivot_longer(cols = -decade, names_to = "Feeling", values_to = "Value")

# Create the interactive plot
p <- plot_ly(data = data_long, x = ~decade, y = ~Value, color = ~Feeling, type = 'scatter', mode = 'lines+markers') %>%
  layout(title = "Trends of Feelings by Decade",
         xaxis = list(title = "Decade"),
         yaxis = list(title = "Average Value"))
p
```
